---
title: "Week 4"
author: "Brennan"
date: "5/11/2020"
output: 
  html_document: 
    keep_md: yes
---

## Video 1
```{r}
library(tidyverse)
```

```{r}
LungCapData <- read.delim("~/Downloads/LungCapData.txt")
```
```{r}
view(LungCapData)
```

```{r}
boxplot(LungCapData$LungCap)
```

# Ho: mu < 8
# one-sided 95% confidence interval for mu

```{r}
t.test(LungCapData$LungCap, mu=8, alternative="less", conf.level=0.95)
```
# two-sided
```{r}
t.test(LungCapData$LungCap, mu=8, alternative="two.side", conf.level=0.95)
```
- two sided is the default argument
```{r}
t.test(LungCapData$LungCap, mu=8, alternative="two.side", conf.level=0.99)
```
```{r}
TEST <- t.test(LungCapData$LungCap, mu=8, alternative="two.side", conf.level=0.99)
```
- Attributes command
```{r}
attributes(TEST)
```
```{r}
TEST$conf.int
TEST$p.value
```

## Video 2
```{r}
boxplot(LungCapData$LungCap~LungCapData$Smoke)
```

# Ho: Mean lung capacity of smokers = of non smokers
# Two-sided test
# assume non-equal variances

```{r}
t.test(LungCapData$LungCap~LungCapData$Smoke, mu=0, alt="two.sided", conf=0.95, var.eq=F,paired=F)
```
- all arguments above are default!
```{r}
t.test(LungCapData$LungCap[LungCapData$Smoke == "no"], LungCapData$LungCap[LungCapData$Smoke == "yes"])
```
```{r}
t.test(LungCapData$LungCap~LungCapData$Smoke, mu=0, alt="two.sided", conf=0.95, var.eq=T,paired=F)
```
- how to decided if we should use var.eq= T or F
1. Look at boxplot and see if variance is comparable
2. Use var() to compare
```{r}
var(LungCapData$LungCap[LungCapData$Smoke == "no"])
var(LungCapData$LungCap[LungCapData$Smoke == "yes"])
```
# Levene's Test
# Ho: population variances are equal

```{r}
library(car)
```
```{r}
leveneTest(LungCapData$LungCap~LungCapData$Smoke)
```
## Mitchell's Data
```{r}
Dull.560_All_Results <- read_csv("~/Downloads/Dull 560_All_Results.csv")
```

```{r}
ggplot(Dull.560_All_Results, aes(Period, RAE, color = Genotype))+
  geom_point() + 
  labs(title = "Period vs Relative Amplitude Error",
      x = "Period (hours)",
       y = "RAE")+
  scale_y_continuous(breaks = c(0, .1, .2, .3, .4, .5, .6, .7, .8, .9, 1))+
  scale_x_continuous(breaks = c(15, 17, 19, 21, 23, 25, 27, 29, 31, 33, 35))
```
```{r}
ggplot(Dull.560_All_Results, aes(Period, RAE, color = Genotype))+
  geom_point() + 
  labs(title = "Period vs Relative Amplitude Error",
      x = "Period (hours)",
       y = "RAE")+
  scale_y_continuous(breaks = c(0, .1, .2, .3, .4, .5, .6, .7, .8, .9, 1))+
  scale_x_continuous(breaks = c(15, 17, 19, 21, 23, 25, 27, 29, 31, 33, 35))+
  facet_wrap(~Genotype)
```
```{r}
RAE_greater <- filter(Dull.560_All_Results, RAE > 0.6)
```
```{r}
col_data <- filter(RAE_greater, Genotype == "col")
T2_95_01_data <- filter(RAE_greater, Genotype == "8x T2 95.01")
T2_96_14_data <- filter(RAE_greater, Genotype == "8x T2 96.14")
T2_97_30_data <- filter(RAE_greater, Genotype == "8x T2 97.30")
```
```{r}
view(col_data)
```
```{r}
view(T2_95_01_data)
```
```{r}
view(T2_96_14_data)
```
```{r}
view(T2_97_30_data)
```
```{r}
summary(col_data$Period)
summary(T2_95_01_data$Period)
summary(T2_96_14_data$Period)
summary(T2_97_30_data$Period)
```
```{r}
Dull_data <- gather(Dull.560_All_Results, "12":"176", key = "Time", value = "Luminescence")
```
```{r}
Dull_data$Time<- as.integer(Dull_data$Time)
str(Dull_data)
```
```{r}
dull_data <- filter(Dull_data, Time > 35)
head(dull_data)
```
```{r}
ggplot(dull_data, aes(Time, Luminescence, color = Genotype))+
  geom_point()+
  labs(title = "Luminescense over Time",
      x = "Time (Zeitberg hours)",
       y = "Luminescence")+
  #scale_y_continuous(breaks = c(0, .1, .2, .3, .4, .5, .6, .7, .8, .9, 1))+
  scale_x_continuous(breaks = seq(36,176, 16))
```
