---
title: "Week_5_rclub"
author: "Brennan"
date: "5/17/2020"
output: 
  html_document: 
    keep_md: yes
---
# 4.3 
```{r}
library(tidyverse)
```

```{r}
LungCapData <- read.delim("~/Downloads/LungCapData.txt")
```


```{r}
boxplot(LungCapData$LungCap~LungCapData$Smoke)
```

### Ho: Median Lung Capcity of Smokers = that of non smokers

```{r}
wilcox.test(LungCapData$LungCap~LungCapData$Smoke, mu = 0, alt="two.sided", conf.int=T, conf.level=0.95, paired=F, exact=T, correct=T)
```
```{r}
wilcox.test(LungCapData$LungCap~LungCapData$Smoke, mu = 0, alt="two.sided", conf.int=T, conf.level=0.95, paired=F, exact=F, correct=T)
```
### Initital settings are the default except conf.int = T

# 4.4
```{r}
cd <- read.csv("~/Downloads/ChickData.csv") 
```

```{r}
boxplot(cd$weight~cd$feed, las =1, ylab="Weight (g)", xlab="feed", main="Weight by feed")
```
### calculate the difference in sample means
```{r}
mean(cd$weight[cd$feed =="casein"])
mean(cd$weight[cd$feed =="meatmeal"])
```
```{r}
test.stat1 <- abs(mean(cd$weight[cd$feed =="casein"])-mean(cd$weight[cd$feed =="meatmeal"]))
```
```{r}
test.stat1
```
```{r}
median(cd$weight[cd$feed =="casein"])
median(cd$weight[cd$feed =="meatmeal"])
```
```{r}
test.stat2 <- abs(median(cd$weight[cd$feed =="casein"])-median(cd$weight[cd$feed =="meatmeal"]))
```
```{r}
test.stat2
```


###Bootstrapping
```{r}
set.seed(112358) # for reproducibility
```
```{r}
n <- length(cd$feed) # number of observations to sample
n
B <- 10000 # of bootstrap samples
variable <- cd$weight #the vairable we will sample from
```
### Now get those boostrap samples (w/o loops)
```{r}
BootstrapSamples <- matrix(sample(variable, size = n*B, replace=T), nrow=n,ncol=B)
```
### lets take a moment to discuss what that code is doing
```{r}
dim(BootstrapSamples)
```   
### now calculate the means for each of the bootstrap samples
```{r}
dim(BootstrapSamples)
```     
```{r}
Boot.test.stat1 <- rep(0, B)
Boot.test.stat2 <- rep(0, B)
```     
   
```{r}
test.stat1; test.stat2
```      
```{r}
round(Boot.test.stat1[1:20],1)
round(Boot.test.stat2[1:20],1)
```    
```{r}
(Boot.test.stat1 >= test.stat1)[1:20]
```  
```{r}
mean(Boot.test.stat1 >= test.stat1)
```  
```{r}
mean(Boot.test.stat2 >= test.stat2)
```  
```{r}
table(cd$feed)
``` 
```{r}
plot(density(Boot.test.stat1), xlab=expression(group("|", bar(Yc)-bad(Ym), "|")))
``` 

# 4.5
```{r}
Obs.Diff.In.Means <- abs(mean(cd$weight[cd$feed =="casein"])-mean(cd$weight[cd$feed =="meatmeal"]))
Obs.Diff.In.Means
```
```{r}
Obs.Diff.In.Medians <- abs(median(cd$weight[cd$feed =="casein"])-median(cd$weight[cd$feed =="meatmeal"]))
Obs.Diff.In.Medians
```
```{r}
set.seed(13579)
n.c <- 12 # number of obs to sample from casein
n.m <- 11 # number of obs to sample from meatmeal
B <- 100000
```
```{r}
Boot.casein <- matrix(sample(cd$weight[cd$feed=="casein"], size=B*n.c, replace=T), ncol=B, nrow=n.c)
```
```{r}
Boot.meatmeal <- matrix(sample(cd$weight[cd$feed=="meatmeal"], size=B*n.m, replace=T), ncol=B, nrow=n.m)
```
```{r}
dim(Boot.casein); dim(Boot.meatmeal) #Checking the dimensions
```
### Check to make sure they aren't empty
```{r}
Boot.casein[1:5, 1:5]
Boot.meatmeal[1:5,1:5]
```
### calculate the diff in means for each of the bootsamples
```{r}
Boot.Diff.In.Means <- colMeans(Boot.casein)-colMeans(Boot.meatmeal)
length(Boot.Diff.In.Means) #check the length
Boot.Diff.In.Means[1:10] #lookin at first ten
```
### now do same for estimate humber 2
```{r}
Boot.Diff.In.Medians <- apply(Boot.casein, MARGIN=2, FUN=median) - apply(Boot.meatmeal, MARGIN=2, FUN=median)
length(Boot.Diff.In.Medians)
Boot.Diff.In.Medians[1:10]
```
### Making the confidence intervals (will be using the percentile method)
```{r}
quantile(Boot.Diff.In.Means, prob=.025)
quantile(Boot.Diff.In.Means, prob=0.975)
```
```{r}
quantile(Boot.Diff.In.Medians, prob=.025)
quantile(Boot.Diff.In.Medians, prob=0.975)
```
# R for DATA Science Questions
## 19.2.1 3
```{r}
avg_NA <- function(x) {mean(is.na(x))}
avg_NA(c(1,2,3,4,5,NA,NA,NA))
```
```{r}
percent_total <- function(x) {
  sm <- sum(x, na.rm = TRUE)
  (x/sm)}
percent_total(c(1,2,3,4,5))
```
```{r}
variation_coeff <- function(x) {
  s<- sd(x, na.rm = TRUE)
  m<- mean(x, na.rm =TRUE)
  (s/m)}
```
```{r}
variation_coeff((c(1,2,3,4,5)))
```
## 19.4.4
- I am sorry. I don't have anything for either of these questions.I just don't know how you could set up an argument of whether or not x is divisible by 3/5 or is at a certain time in comparison to current time. I looked up code online, but I don't get it. :p
## 21.2.1 1
A.
```{r}
mtcars_avg <- vector("double", ncol(mtcars))  
for (i in seq_along(mtcars)) {            
  mtcars_avg[[i]] <- mean(mtcars[[i]])     
}
mtcars_avg
```
B.
```{r}
iris
```
```{r}
iris$Species = as.character(iris$Species) 
iris_types <- vector("character", ncol(iris))  # 1. output
for (i in seq_along(iris)) {            # 2. sequence
  iris_types[[i]] <- typeof(iris[[i]])      # 3. body
}
iris_types
```
- I don't know what's up with this one. It's correct for the first four, but for the fifth column it says its an integer even though it is a factor. And I can't make a vector out of a factor for some reason. I converted Species to character just because all the inputs are names, plus it works with the loop I made.

## 21.3.5 3
```{r}
iris_2 <- select(iris, Sepal.Width, Sepal.Length, Petal.Length, Petal.Width)
iris_2
```
```{r}
iris_2_means <- vector("list", length(iris_2))
for (i in seq_along(iris_2)) {
  iris_2_means[[i]] <- mean(iris_2[[i]])
}
iris_2_means
```
```{r}
iris_2_means_map <- map_dbl(iris_2, mean)
iris_2_means_map
```
- I was unable to figure out how to name the subsections of the list. So, I just used the map_dbl function cause I knew the column names would be included. Also, I didn't know how else to exclude the Species column other than using select beforehand.
## 21.5.3 1
A.
```{r}
mtcars_avg_2 <- map_dbl(mtcars, mean)
mtcars_avg_2
```
B.
```{r}
iris_types_2 <- map_chr(iris, typeof)
iris_types_2 
```










